### 2024-01-07 doc/Thesis/chapter/020-theory-materials.tex
rough corrections finished

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}/\gls{vis}/\gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
\td{FORMATTING: In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
In other materials light moves with the velocity $v=c/n(\lambda)$, where $n(\lambda)$
is the refractive index which is dependent on the wavelength $\lambda$. 
%is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:}
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}/\gls{vis} with valence electrons, \gls{ir} with 
%\td{it's adsorbed by certain groups?)} 
vibrations of certain groups, microwaves with molecular rotations and radio with electron and nuclear spins. 
%
% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}/\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, \td{the energy of the photon must be the same as the difference between two electronic states, a lower populated and a higher empty orbital.}
The electron will then be excited into a energetically higher orbital.
Secondly, the electronic spin state of the molecule has to be the same before and after, otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}/\gls{vis}/\gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
\td{FORMATTING: In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
In other materials light moves with the velocity $v=c/n(\lambda)$, where $n(\lambda)$
is the refractive index which is dependent on the wavelength $\lambda$. 
%is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:}
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}/\gls{vis} with valence electrons, \gls{ir} with 
%\td{it's adsorbed by certain groups?)} 
vibrations of certain groups, microwaves with molecular rotations and radio with electron and nuclear spins. 
%
% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}/\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, the energy of the photon must be the same as the difference between two electronic states. %, a lower populated and a higher empty orbital.}
The electron will then be excited into a energetically higher orbital.
Secondly, the electronic spin state of the molecule has to be the same before and after, otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.

### 2024-01-07 doc/Thesis/chapter/021-theory-calculations.tex
rough corrections finished

A \gls{ga} is a search algorithm that uses principles of natural selection and genetics (mutations and recombination) to optimize a search space. A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions. The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes. This process is repeated until a \td{satisfactory} solution is found.\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms:"}

>>>>

A \gls{ga} is a search algorithm that uses principles of natural selection and genetics (mutations and recombination) to optimize a search space. A GA starts with a population of randomly generated solutions, or chromosomes, and then proceeds to breed them together to create new solutions. The new solutions are then tested for fitness, and the best solutions are selected to create the next generation of chromosomes. This process is repeated until a satisfactory solution is found (mostly after a predefined number of repetitions).\footnote{This paragraph was written by GPT3\cite{Liu2021gpt} given the input "Introduction to genetic algorithms:"}

### 2024-01-07 doc/Thesis/chapter/03-experimental.tex
rough corrections finished

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{materials section and sources (incl. purities is missing!) }
In this section the used chemicals, substrates, experimental procedures and any used lab equipment are described. 
\td{All chemicals used in this work are of reagent-grade purity and without further purification.}
%\td{Also, the long, exhaustive path to the base solution is described}
%\td{The experiments can be split into three sections: }
First, the base recipe and the base process settings were explored. 
Then, the analysis of samples is discussed and the boundaries for the optimization were investigated during pre-optimization.
Finally, the experiments for the optimization were performed.

\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
squared glass plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
\gls{ito} plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
\gls{fto} plates (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
%
Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
The conducting substrate allows for easy measurement of electric conductance in vertical direction.
Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repell further electrons without a conducting substrate.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
\td{is that the usual procedure for steel?}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step.

@@

%The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four buthanolic solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
Solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before 
starting the optimization of the process variables
%the \td{particle swarm optimisation} started 
- the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal 
complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%C          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Doctor blading}
\label{sec:exp-db}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied to create a valley in between. 
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

@@

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
		\caption{}
		\label{fig:micro1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
		\caption{}
		\label{fig:micro2}
	\end{subfigure}
	\begin{subfigure}{\textwidth}
		\centering
		\begin{circuitikz} \draw
			(0,0) to[european voltage source] (0,2)
			to[ammeter] (2,2) 
			to[generic,l=W] (4,2) 
			to[generic,l=Au] (6,2) 
			to[generic,l=Al] (8,2)
			-- (8,2)
			to[generic,l=ZrO$_2$] (8,0)
			-- (8,0)
			to[generic,l=steel] (6,0)
			to[generic,l=Ag] (4,0)
			to[generic,l=Au] (2,0) 
			to[generic,l=W] (0,0) 
				;
		\end{circuitikz}
		\caption{}
		\label{fig:circuit}
	\end{subfigure}
	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
	\label{fig:micro}
	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
	(c) From the voltage source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.\td{(what is XXX circuit?)}}
\end{figure}

@@

using the Plackett-Burman\cite{Plackett1946} design implemented in the \td{\texttt{python3}}
library texttt{pyDOE} \td{(Version 0.3.8)}; 

@@

After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see table \ref{tab:pre-opt1}).

@@

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \td{\gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
(but why?)} because of much better \td{solution stability. (how did you test this?? see section \ref{sec:res-mat})}
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable passivization results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{materials section and sources (incl. purities is missing!) }
In this section the used chemicals, substrates, experimental procedures and any used lab equipment are described. 
%\td{
All chemicals used in this work are of reagent-grade purity and without further purification. 
%}
%\td{Also, the long, exhaustive path to the base solution is described}
%\td{The experiments can be split into three sections: }
First, the base recipe and the base process settings were explored. 
Then, the analysis of samples is discussed and the boundaries for the optimization were investigated during pre-optimization.
Finally, the experiments for the optimization were performed.

\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
squared glass plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
\gls{ito} plates (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich, 
\gls{fto} plates (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
%
Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
The conducting substrate allows for easy measurement of electric conductance in vertical direction.
Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repell further electrons without a conducting substrate.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
%\td{is that the usual procedure for steel?}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step (cf. \cite{YAMASHITA2018,Kohli2010}).

@@

%The \td{\gls{1f}} was closest to the recipe proposed by Hu~et~al.~\cite{Hu2016}. 
The other four buthanolic solutions (\gls{2f}, \gls{3f}, \gls{4f} and \gls{5f}) were similar 
but with higher concentrations of \gls{zrpro} (see table \ref{tab:rec2})
with the aim of producing thicker layers.
%\td{p34}
Solvents (butane-1,2-diol, \gls{buoh} and Propan-1-ol) and chelating agents 
(\gls{acac} and citric acid) were tested and later in the process - just before 
starting the optimization of the process variables
%the \td{particle swarm optimisation} started 
- the stabilization compound (\gls{acoh}) was changed to \gls{ipo}.
The most promising combination of solvent, chelating agent and stabilization reagent was 
\gls{buoh}, \gls{acac} and \gls{ipo}, respectively, which was used for the final optimization.
\ds{
The main differences between the used recipe and the recipe mentioned in \cite{Hu2016} were 
\td{precursor (transition metal complex \gls{zrpro}	\gls{vs} post-transition metal complex aluminium isopropoxide \ch{Al(PrO)3}), solvent (\gls{buoh} \gls{vs} 2-ethoxyethanol \ch{EtOEtOH}), reaction temperature 
(room temperature \gls{vs} \SI{105}{\celsius}), stirring time (15/15/\SI{30}{\minute}
\gls{vs} 30/30/\SI{120}{\minute}), application process (doctor blading \gls{vs} spin coating), 
the heat treatment between layers (\SI{200}{\celsius} \gls{vs} \SI{200}{\celsius} and then \SI{400}
{\celsius}) and the calcination temperature (\SI{400}{\celsius} \gls{vs}
\SI{500}{\celsius}).
( so everything is different!! now I'm confused? you dream up a recipe and optimize that? not how I would do that! also: quite a difference between alpro3 and zrpro4)}
}
%me          hu
%Zr(OPr)4    Al(iPrO)3   
%1-BuOH      2-MeO-EtOH  
%RT          80-105
%15-15-30    30-30-120
%C          spin coating
%200C        200/400C
%400C        500C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Blade Coating}
\label{sec:exp-db}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied to create a valley in between. 
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

@@

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
		\caption{}
		\label{fig:micro1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
		\caption{}
		\label{fig:micro2}
	\end{subfigure}
	\begin{subfigure}{\textwidth}
		\centering
		\begin{circuitikz} \draw
			(0,0) to[european voltage source] (0,2)
			to[ammeter] (2,2) 
			to[generic,l=W] (4,2) 
			to[generic,l=Au] (6,2) 
			to[generic,l=Al] (8,2)
			-- (8,2)
			to[generic,l=ZrO$_2$] (8,0)
			-- (8,0)
			to[generic,l=steel] (6,0)
			to[generic,l=Ag] (4,0)
			to[generic,l=Au] (2,0) 
			to[generic,l=W] (0,0) 
				;
		\end{circuitikz}
		\caption{}
		\label{fig:circuit}
	\end{subfigure}
	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
	\label{fig:micro}
	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
	(c) From the voltage source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe. }%\td{(what is XXX circuit?)}}
\end{figure}

@@

using the Plackett-Burman\cite{Plackett1946} design implemented in the \texttt{python3} (version 3.9)
library \texttt{pyDOE} (version 0.3.8); 

@@

After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see appendix \ref{sec:app-pre-emma}).
\ds{
table \ref{tab:pre-opt1}).

@@

}

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
because of much better solution stability and similar electric properties of resulting layers (how did you test this?? see appendix \ref{sec:app-pre-emma}).
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable passivization results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi
